\epigraph{None of us get out of here alive.}{Jim Morrison of the Doors}
\epigraph{Political language ... is designed to make lies sound truthful and murder respectable, and to give an appearance of solidity to pure wind.}{George Orwell}
\epigraph{I never let my schooling get in the way of my education.}{Mark Twain}
\epigraph{Leave death nothing but a burnt out castle.}{Zorba The Greek}
\epigraph{Bayesian analysis can be summarized in just two concepts. Use probability distributions to represent the uncertainty in your model parameters. Then use Bayes theorem to update those probabilities given the data you have.}{Osvaldo Martin \url{https://towardsdatascience.com/probability-concepts-explained-bayesian-inference-for-parameter-estimation-90e8930e5348}}
\epigraph{I hear and I forget. \\ I see and I remember. \\ I do and I understand.}{Confucius}
\epigraph{Science is more than a body of knowledge; it is a way of thinking. The method of science, as stodgy and grumpy as it may seem, is far more important than the findings of science.}{Carl Sagan}
\epigraph{No body of data tells us all we need to know about its own analysis.}{John Tukey}
\epigraph{Probability theory is nothing but common sense reduced to calculation.}{Piere Simon Laplace}
\epigraph{Sample sizes are never large. If N is too small to get a sufficiently-precise estimate, you need to get more data (or make more assumptions). But once N is `large enough', you can start subdividing the data to learn more (for example, in a public opinion poll, once you have a good estimate for the entire country, you can estimate among men and women, northerners and southerners, different age groups, etc etc). N is never enough because if it were `enough' you'd already be on to the next problem for which you need more data.}{Andrew Gelman (blog entry, 31 July 2005)}
\epigraph{Systematic error has meaning only if we understand by the true value something different from the [inferred] parameter. It is therefore an additional parameter, and requires a significance test for its assertion. There is no epistemological difference between the Smith effect [a parameter in a model] and Smith’s systematic error; the difference is that Smith is pleased to find the former, while he may be annoyed at the discovery of the latter.}{Jeffreys 1939, 1961}
\epigraph{Perpetual optimism is a force multiplier.}{Colin Powell}
\epigraph{Do not worry about your difficulties in Mathematics. I can assure you mine are still greater.}{Albert Einstein}
\epigraph{Weak people revenge. Strong people forgive. Intelligent people Ignore.}{Albert Einstein} 
\epigraph{try not to get involved in the business of prediction. It’s a quick way to look like an idiot.}{Warren Ellis}
\epigraph{Machine learning will cause every successful IPO win in five years.}{—Eric Schmidt, Google executive chairman, keynote speech, Cloud Computing Platform conference, 2016}
\epigraph{The only relevant test of the validity of a hypothesis is comparison of its predictions with experience}{Milton Friedman, Essays in Positive Economics (University of Chicago Press, 1953)}
\epigraph{You don’t learn to walk by following rules. You learn by doing and by falling over.}{Richard Branson, http://mng.bz/oVgd}
\epigraph{Numbers have an important story to tell. They rely on you to give them a clear and convincing voice.}{Stephen Few, IT innovator, teacher, and consultant}
\epigraph{With four parameters I can fit an elephant, and with five I can make him wiggle his trunk.}{John von Neumann, mathematician, physicist, computer scientist, and polymath}
\epigraph{The pooling operation used in convolutional neural networks is a big mistake, and the fact that it works
so well is a disaster.}{Geoffrey Hinton, from ``Ask Me Anything'' on Reddit}
\epigraph{Man is a slow, sloppy, and brilliant thinker; computers are fast, accurate, and stupid.}{John Pfeiffer, in Fortune, 1961}
\epigraph{There’s something magical about Recurrent Neural Networks.}{Andrej Karpathy, “The Unreasonable Effectiveness of Recurrent Neural Networks,” http://mng.bz/V PW}
\epigraph{Whether we are based on carbon or on silicon makes no fundamental difference; we should each be treated with appropriate respect.}{Arthur C. Clarke, 2010: Odyssey Two (1982)}
\epigraph{Friends don’t spy; true friendship is about privacy, too.}{Stephen King, Hearts in Atlantis (1999)}
\epigraph{Whether you believe you can do a thing or not, you are right.}{Henry Ford, automobile manufacturer}
\epigraph{Amateurs sit and wait for inspiration, the rest of us just get up and go to work.}{Stephen King}
\epigraph{There is no failure unless one stops.}{Ray Bradbury}
\epigraph{You can't think yourself out of a writing block; you have to write yourself out of a thinking
block.}{John Rogers}
\epigraph{My ideas usually come not at my desk writing but in the midst of living}{Anais Nin}
\epigraph{Almost all good writing begins with terrible first efforts. You need to start somewhere.}{Anne Lamott}
\epigraph{This is how you do it: You sit down at the keyboard and you put one word after another until it's done. It's that easy, and that hard}{Neil Gaiman}
\epigraph{Just write every day of your life. Read intensely. Then see what happens. Most of my
friends who are put on that diet have very pleasant careers}{Ray Bradbury}
\epigraph{Write freely and as rapidly as possible and throw the whole thing on paper. Never correct
or rewrite until the whole thing is done. Rewrite in process is usually found to be an
excuse for not moving on. It also interferes with flow and rhythm which can only come
from a kind of unconscious association with the material.}{John Steinbeck}
\epigraph{Your desire to write grows with writing.}{Desiderius Erasmus}
\epigraph{The scariest moment is always just before you start}{Stephen King}
\epigraph{It is normal for your writing practice to have cyclic ups and downs. Don't be discouraged; all writers must overcome writing resistance at some time or another. If your writing practice is not where you want it to be, think about what is holding you back (see Box 1), then develop strategies to overcome your resistance to writing. Also, periodically accelerate your writing practice by joining a writing retreat or planning a weekend away to write. Truly, the only way to maintain your writing productivity is to keep writing.}{}
\epigraph{Note that it may not be necessary to follow all the rules all the time; experiment and find what works for your writing practice. If you find your writing sessions are becoming less productive because you are facing new hurdles to writing (see Box 1), refine your writing practice using Rules 1-10}{Peterson et al. 2018 https://doi.org/10.1371/journal.pcbi.1006379}
\epigraph{The SMART criteria: specific, measurable, action-oriented, reasonable, time-bound}{}
\epigraph{If you have difficulty ignoring the siren call of new emails or the internet, turn it off for the duration of your writing time. Constant interruptions disrupt your thinking and eat up your time for writing.}{Peterson et al. 2018 https://doi.org/10.1371/journal.pcbi.1006379}
\epigraph{The best way to predict to the future is to the shape the future}{Gabor 1963 Inventing The Future}
\epigraph{A man has to know his limitations.}{Dirty Harry}
\epigraph{Hope is not a strategy!}{Lena Wen, COVID-19 emergency room physician}
epigraph{If I am not for myself, who will be for me? If I am not for others, what am I? And if not now, when?}{Rabbi Hillel}
\epigraph{I fear not the man who has practiced 10,000 kicks once, but I fear the man who has practiced one kick 10,000 times.}{Bruce Lee}
\epigraph{Darkness cannot drive out darkness; only light can do that. Hate cannot drive out hate; only love can do that.}{Martin Luther King, Jr.}
\epigraph{You cannot escape the responsibility of tomorrow by evading it today.}{Abraham Lincoln}
\epigraph{Before you speak ask yourself if what you are going to say is true, is kind, is necessary, is helpful. If the answer is no, maybe what you are about to say should be left unsaid.}{Bernard Meltzer}
\epigraph{You can search throughout the entire universe for someone who is more deserving of your love and affection than you are yourself, and that person is not to be found anywhere. You yourself, as much as anybody in the entire universe deserve your love and affection.}{Buddha}
\epigraph{You may not always have a comfortable life and you will not always be able to solve all of the world's problems at once but don't ever underestimate the importance you can have because history has shown us that courage can be contagious and hope can take on a life of its own.}{Michelle Obama}
\epigraph{If you tell people where to go, but not how to get there, you'll be amazed at the results.}{George S. Patton}
\epigraph{A good plan violently executed now is better than a perfect plan executed next week.}{George S. Patton}
\epigraph{Don't tell people how to do things, tell them what to do and let them surprise you with their results.}{George S. Patton}
\epigraph{The object of war is not to die for your country but to make the other bastard die for his.}{George S. Patton}
\epigraph{Nobody ever defended anything successfully, there is only attack and attack and attack some more.}{George S. Patton}
\epigraph{In politics, nothing happens by accident. If it happens, you can bet it was planned that way.}{Franklin D. Roosevelt}
\epigraph{We are shaped by our thoughts; we become what we think. When the mind is pure, joy follows like a shadow that never leaves.}{Buddha}
\epigraph{Yesterday is not ours to recover, but tomorrow is ours to win or lose.}{Lyndon B. Johnson}
\epigraph{Live as if you were to die tomorrow. Learn as if you were to live forever.}{Mahatma Gandhi}
\epigraph{Accept the challenges so that you can feel the exhilaration of victory.}{George S. Patton}
\epigraph{Better to fight for something than live for nothing.}{George S. Patton}
\epigraph{Always do everything you ask of those you command.}{George S. Patton}
\epigraph{Prepare for the unknown by studying how others in the past have coped with the unforeseeable and the unpredictable.}{George S. Patton}
\epigraph{If everyone is thinking alike, then somebody isn't thinking.}{George S. Patton}
\epigraph{Wars may be fought with weapons, but they are won by men. It is the spirit of men who follow and of the man who leads that gains the victory.}{George S. Patton}
\epigraph{If we take the generally accepted definition of bravery as a quality which knows no fear, I have never seen a brave man. All men are frightened. The more intelligent they are, the more they are frightened.}{George S. Patton}
\epigraph{Success is how high you bounce when you hit bottom.}{George S. Patton}
\epigraph{A pint of sweat, saves a gallon of blood.}{George S. Patton}
\epigraph{There is a time to take counsel of your fears, and there is a time to never listen to any fear.}{George S. Patton}
\epigraph{The secret of your success is determined by your daily agenda.}{John C. Maxwell}
\epigraph{Your attitude towards failure determines your altitude after failure.}{John C. Maxwell}
\epigraph{People who add value to others do so intentionally. I say that because to add value, leaders must give of themselves, and that rarely occurs by accident.}{John C. Maxwell}
\epigraph{A leader is one who knows the way, goes the way, and shows the way.}{John C. Maxwell}
\epigraph{The greatest day in your life and mine is when we take total responsibility for our attitudes. That's the day we truly grow up.}{John C. Maxwell}
\epigraph{Failed plans should not be interpreted as a failed vision. Visions don't change, they are only refined. Plans rarely stay the same, and are scrapped or adjusted as needed. Be stubborn about the vision, but flexible with your plan. }{John C. Maxwell}
\epigraph{Self-centered leaders manipulate when they move people for personal benefit. Mature leaders motivate by moving people for mutual benefit.}{John C. Maxwell}
\epigraph{If you are a leader, you should never forget that everyone needs encouragement. And everyone who receives it - young or old, successful or less-than-successful, unknown or famous - is changed by it.}{John C. Maxwell}
\epigraph{All good leaders are connectors. They relate well and make people feel confident about themselves and their leader.}{John C. Maxwell}
\epigraph{We choose what attitudes we have right now. And it's a continuing choice.}{John C. Maxwell}
\epigraph{The greatest mistake we make is living in constant fear that we will make one.}{John C. Maxwell}
\epigraph{Learn to say 'no' to the good so you can say 'yes' to the best.}{John C. Maxwell}
\epigraph{Educators take something simple and make it complicated. Communicators take something complicated and make it simple.}{John C. Maxwell}
\epigraph{To add value to others, one must first value others.}{John C. Maxwell} 
\epigraph{A man must be big enough to admit his mistakes, smart enough to profit from them, and strong enough to correct them.}{John C. Maxwell}
\epigraph{In the end, people are persuaded not by what we say, but by what they understand.}{John C. Maxwell}
\epigraph{The first time you say something, it's heard. The second time, it's recognized, and the third time it's learned.}{John C. Maxwell}
\epigraph{Good executives never put off until tomorrow what they can get someone else to do today.}{John C. Maxwell}
\epigraph{Without failure there is no achievement.}{John C. Maxwell}
\epigraph{Everything rises and falls on leadership.}{John C. Maxwell}
\epigraph{... leaders must bring their vision and the aspirations of the people they lead together in a way that benefits everyone.}{John C. Maxwell}
\epigraph{Good leaders must communicate vision clearly, creatively, and continually. However, the vision doesn't come alive until the leader models it.}{John C. Maxwell}
\epigraph{To remain a credible leader, I must always work first, hardest, and longest on changing myself. This is neither easy nor natural, but it is essential.}{John C. Maxwell}
\epigraph{Ideas have a short shelf life. You must act on them before the expiration date.}{John C. Maxwell}
\epigraph{As a leader, the first person I need to lead is me. The first person that I should try to change is me.}{John C. Maxwell}
\epigraph{Most people don't like change. They revolt against it unless they can clearly see the advantage it brings. For that reason, when good leaders prepare to take action or make changes, they take people through a process to get them ready for it.}{John C. Maxwell}
\epigraph{Self-centered leaders manipulate when they move people for personal benefit. Mature leaders motivate by moving people for mutual benefit.}{John C. Maxwell}
\epigraph{To be yourself in a world that is constantly trying to make you something else is the greatest accomplishment.}{Ralph Waldo Emerson}
\epigraph{When one door closes, another opens; but we often look so long and so regretfully upon the closed door that we do not see the one which has opened for us.}{Alexander Graham Bell}
\epigraph{Before anything else, preparation is the key to success.}{Alexander Graham Bell}
\epigraph{The most successful men in the end are those whose success is the result of steady accretion.}{Alexander Graham Bell}
\epigraph{A man, as a general rule, owes very little to what he is born with - a man is what he makes of himself.}{Alexander Graham Bell}
\epigraph{It's not that I'm so smart, it's just that I stay with problems longer.}{Albert Einstein}
\epigraph{Anyone who has never made a mistake has never tried anything new.}{Albert Einstein}
\epigraph{The true sign of intelligence is not knowledge but imagination.}{Albert Einstein}
\epigraph{The world is a dangerous place to live; not because of the people who are evil, but because of the people who don't do anything about it.}{Albert Einstein}
\epigraph{Only two things are infinite, the universe and human stupidity, and I'm not sure about the former.}{Albert Einstein}
\epigraph{Our task must be to free ourselves by widening our circle of compassion to embrace all living creatures and the whole of nature and its beauty.}{Albert Einstein}
\epigraph{The only source of knowledge is experience.}{Albert Einstein}
\epigraph{Weakness of attitude becomes weakness of character.}{Albert Einstein}
\epigraph{No amount of experimentation can ever prove me right; a single experiment can prove me wrong.}{Albert Einstein}
\epigraph{Few are those who see with their own eyes and feel with their own hearts.}{Albert Einstein}
\epigraph{Without deep reflection one knows from daily life that one exists for other people.}{Albert Einstein}
\epigraph{Reality is merely an illusion, albeit a very persistent one.}{Albert Einstein}
\epigraph{Small is the number of people who see with their eyes and think with their minds.}{Albert Einstein}
\epigraph{Nationalism is an infantile disease. It is the measles of mankind.}{Albert Einstein}
\epigraph{Any man who can drive safely while kissing a pretty girl is simply not giving the kiss the attention it deserves.}{Albert Einstein}
\epigraph{Morality is of the highest importance - but for us, not for God.}{Albert Einstein}
\epigraph{Look deep into nature, and then you will understand everything better.}{Albert Einstein}
\epigraph{As far as the laws of mathematics refer to reality, they are not certain, and as far as they are certain, they do not refer to reality.}{Albert Einstein}
\epigraph{Anyone who doesn't take truth seriously in small matters cannot be trusted in large ones either.}{Albert Einstein}
\epigraph{It is the supreme art of the teacher to awaken joy in creative expression and knowledge.}{Albert Einstein}
\epigraph{Intellectuals solve problems, geniuses prevent them.}{Albert Einstein}
\epigraph{Prolific academics create writing time \emph{where none exists} and then carefully \emph{protect it} from intrusion.}{Johnson and Mullen \cite{Johnson2007WriteToTheTopHowToBecomeAProlificAcademic}}
\epigraph{...enabling student learning defines you as a teacher.}{Johnson and Mullen \cite{Johnson2007WriteToTheTopHowToBecomeAProlificAcademic}}
\epigraph{How quick are we to learn: that is, to imitate what others have done or thought before. And how slow to understand: that is, to see the deeper connections.}{Frits Zernike}
\epigraph{Academic departments generally lack the resources that encourge aculty collaboration and creativity in teaching assignments, and they are constrained by inflexible evaluation-and-reward structures.}{Johnson and Mullen \cite{Johnson2007WriteToTheTopHowToBecomeAProlificAcademic}}
\epigraph{Paraphrased: Use your matrix of assigned duties and writing commitments to decline inivtations that fall outside of your matrix.}{Johnson and Mullen \cite{Johnson2007WriteToTheTopHowToBecomeAProlificAcademic}}
\epigraph{...tenured faculty who obtain competitive grants and book contracts have leverage and can neogotiate releases from teaching.}{Johnson and Mullen \cite{Johnson2007WriteToTheTopHowToBecomeAProlificAcademic}}
\epigraph{It is ironic that most important activity in the academy, as far as tenure, promotion, and recognition in the field are concerned, is also the most invisible and haphazardly scheuduled.}{Johnson and Mullen \cite{Johnson2007WriteToTheTopHowToBecomeAProlificAcademic}}
\epigraph{It must be borne in mind that the tragedy of life doesn’t lie in not reaching your goal. The tragedy lies in having no goal to reach. It isn’t a calamity to die with dreams unfulfilled, but it is a calamity not to dream. It is not a disaster to be unable to capture your ideal, but it is a disaster to have no ideal to capture. It is not a disgrace not to reach the stars, but it is a disgrace to have no stars to reach for. Not failure, but low aim is sin.}{Benjamin Elijah Mays}
\epigraph{Whatever you do,strive to do it so well that no man living and no man dead and no man yet to be born could do it any better.}{Benjamin Elijah Mays}
\epigraph{Whatever you do, strive to do it so well that no man living and no man dead and no man yet to be born could do it any better.}{Benjamin Elijah Mays}
\epigraph{We have mastered the air, conquered the sea, annihilated distance, and prolonged life, but we are not wise enough to live on this earth without war and without hate. All knowledge leads to an impasse.}{Benjamin Elijah Mays}
\epigraph{And I have a very good principle for helping people keep at it, which is either your intuitions are good or they're not. If your intuitions are good, you should follow them and you'll eventually be successful. If your intuitions are not good, it doesn't matter what you do.}{Geoffrey Hinton}
\epigraph{Yes, it's true that when you're trying to replicate a published work, you discover all over little tricks necessary to make it work.}{Geoffrey Hinton}
\epigraph{Right, but there is one thing, which is, if you think it's a really good idea, and other people tell you it's complete nonsense, then you know you're really on to something.}{Geoffrey Hinton}
\epigraph{You might as well trust your intuitions. There's no point not trusting them.}{Geoffrey Hinton}
\epigraph{You have to have order in order to have innovation.}{Ocean Vuong, BBC interview Sept.8, 2020}
\epigraph{Drafting is a collaboration with yourself.}{Ocean Vuong, BBC interview Sept.8, 2020}
\epigraph{Revision is the practice of care. }{Ocean Vuong, BBC interview Sept.8, 2020}
\epigraph{It was as useless to fight against the interpretations of ignorance as to whip the fog.}{George Eliot, Middlemarch}
\epigraph{When talent is lacking, habit will often suffice.}{James Clear}
\epigraph{Just begin and the mind grows heated; continue, and the task will be completed!}{}
\epigraph{The older I grow, the more I distrust the familiar doctrine that age brings wisdom.}{Henry L. Mencken}
\epigraph{ The paper will outline some of the history of this hierarchical technique with emphasis on the contributions by I. J. Good because I have read every word written by him.}{I. J. Good}
\epigraph{A small daily task, if it be really daily, will beat the labours of a spasmodic Hercules.} 
{Anthony Trollope}
\epigraph{If your experiment needs a statistician, you need a better experiment.}{Ernest Rutherford}
\epigraph{All science is either physics or stamp collecting.}{Ernest Rutherford}
\epigraph{A theory that you can't explain to a bartender is probably no damn good.}{Ernest Rutherford}
\epigraph{That which is not measurable is not science. That which is not physics is stamp collecting.}{Ernest Rutherford}
\epigraph{Every good laboratory consists of first rate men working in great harmony to insure the progress of science; but down at the end of the hall is an unsociable, wrong-headed fellow working on unprofitable lines, and in his hands lies the hope of discovery.}{Ernest Rutherford}
\epigraph{The more physics you have the less engineering you need.
}{Ernest Rutherford}
\epigraph{I am a great believer in the simplicity of things and as you probably know I am inclined to hang on to broad & simple ideas like grim death until evidence is too strong for my tenacity.}{Ernest Rutherford}
\epigraph{It is essential for men of science to take an interest in the administration of their own affairs or else the professional civil servant will step in - and then the Lord help you.}{Ernest Rutherford}
\epigraph{I have to keep going, as there are always people on my track. I have to publish my present work as rapidly as possible in order to keep in the race. The best sprinters in this road of investigation are Becquerel and the Curies.}{Ernest Rutherford}
\epigraph{You should never bet against anything in science at odds of more than about 10-12 to 1.}{Ernest Rutherford}
\epigraph{Gentlemen, we have run out of money. It is time to start thinking.}{Ernest Rutherford}
\epigraph{Else if you would be a man speak what you think to-day in words as hard as cannon balls, and to-morrow speak what tomorrow thinks in hard words again, though it contradict every thing you said to-day.}{Ralph Waldo Emerson}
\epigraph{Do not despise these small beginnings, for the Lord rejoices to see the work begin.}{ Zechariah 4:10}
\epigraph{Preferences are optional and subject to constraints, whereas constraints are neither optional nor subject to preferences.}{Marko Papic, `Geopolitical Alpha'}
\epigraph{Every man must decide whether he will walk in the light of creative altruism or in the darkness of destructive selfishness.}{Martin Luther King, Jr.}
\epigraph{One cannot think without writing.}{Niklas Luhmann 1992, ``Kommunikation mit Zettelkästen. Ein Erfahrungsbericht.'' In Universität als Milieu. Kleine Schriften., edited by Andre Kieserling, 53–61. Bielefeld: Haux.}
\epigraph{Notes on paper, or on a computer screen [...] do not make contemporary physics or other kinds of intellectual endeavor easier, they make it possible … no matter how internal processes are implemented [...you..] need to understand the extent to which the mind is reliant upon external scaffolding.}{Levy 2011, Neil. 2011. ``Neuroethics and the Extended Mind.'' In Judy Illes and B. J. Sahakian (Ed.), Oxford Handbook of Neuroethics, 285–94, Oxford University Press.}
\epigraph{The Zettelkasten is much more effort and time consuming than writing books}{Niklas Luhmann, Shortcuts}
\epigraph{Notes aren’t a record of my thinking process. They are my thinking process.}{Richard Feynman}
\epigraph{If you see someone without a smile, give them yours.}{Dolly Parton}
\epigraph{That is leadership. It means being the first to do something in an attempt to establish a new norm.}{Edward Snowden, 31 May 2019, Live from Russia | Dalhousie University.}
\epigraph{Tranlastional research might be in vogue but remember that if you do not do foundational basic discovery research, you will not have anything to translate.}{David Atkinson}
\epigraph{You will write only as well as you make yourself write.}{William Zinseer (2006) \emph{On Writing Well}}
\epigraph{Few people realize how badly they write.}{William Zinseer (2006) \emph{On Writing Well}}
\epigraph{We are entitled to our voices but not to our readers: Pretentious, haughty, and patronizing writing is a turn-off.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{... writing for impact seeks to influence peers, to change minds about something that the field cares about.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{... The first is to plan and reflect: Writing good papers requires planning, sweating the small stuff, and overthinking everything.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Many good papers get rejected because they were pointed at the wrong audience.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Writing for impact is trying to change the conversation: pointing out somethg new and interesting, changing how people think about a familiar problem, refining the field's vocabulary, adding new concepts and tools. }{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Many nice papers end up underplaced and underappreciated, usually because of common mistakes or a lack of craft.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Because most of our work is in teams, we need tools for writing collaborative papers quickly and effectively.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{... the proliferation of journal has made the best ones prominent--when there's too much information, people will tune much of it out.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Another virtue of choosing a journal before you do the research is that you can craft the project to appeal to the audience that you want to influcence.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Because it is rational to expect rejection--the odds are always against you--experienced writers plan resubmissions before their submissions.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{... with writing: I learned nearly everything I know from reading books about writing.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Ignorance never stopped people from having strong opinions...}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Confident writing feels assertive--it seeks to make a point and change minds; defensive writing feels timid--it seeks to stave off criticism and avoid disaster.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Even if you rarely write work with a casual sound, learning how to do so will teach you important mechanics and make your formal writing tighter.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{A confident writerm in contrast, comes across as a reasonable person with the credibility that comes from reading widely, thinking logically, and respecting widely discipline's norms for scholarship.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{Parentheses work but they mute rather than emphasize.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
\epigraph{A rough but effective test of sentence variablity is punctuation variability. If a page of text has dashes, semicolons, colons, and question marks, ut usually has good sentence variability.}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{}{Paul J. Silvia (2015) \emph{Write It Up.} American Psychological Association.}
%\epigraph{When students cheat on exams, it's because pur school system values grades more than students value learning.}{Neil deGrasse Tyson}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
%\epigraph{}{}
